---
title: "README"
author: "Xiaxian Ou"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    number_sections: false
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, eval=F)
```

**flexPaths**: flexible causal path-specific effect

-   two decomposition strategy

-   flexible paths

-   flexible models

-   flexible estimators

Install this package:

```{r}
library(devtools)
install_github("xxou/flexPaths")
```



# 1. single treatment

## path fit
```{r}
data("singTreat")
EIF_fit <- pathsFit(data = singTreat, A = "treat", Y = "outcome1", cov_x = c("X1", "X2"),
                    M.list = list(M1 = "med1", M2 = c('med2_1', 'med2_2'), M3 = 'med3'),
                    estimation = "EIF",
                    model.outcome = list(~ glm(family = gaussian())),
                    model.propensity = ~ bart(verbose = FALSE, ndpost = 200)
)
```

## mediation effects through each mediator

```{r}
effect_results1 <- pathsEffect(pathsFit = EIF_fit, decomposition = "refer0", scale = "diff", CI_level = 0.95)
effect_results2 <- pathsEffect(pathsFit = EIF_fit, decomposition = "refer0", scale = "diff", CI_level = 0.95, nboot = 100, m.cores = 6)

effect_results3 <- pathsEffect( pathsFit = EIF_fit, decomposition = "sequential", scale = "diff", CI_level = 0.95)
```


## flexible paths for single treatment

potential outcome:
```{r}
potential_outcome0 <- flexPotential(pathsFit = EIF_fit, active = c(0, 0, 0, 0))
potential_outcome1 <- flexPotential(pathsFit = EIF_fit, active = c(1, 0, 1, 1))
potential_outcome2<- flexPotential(pathsFit = EIF_fit, active = c(1, 0, 0, 1))
```

use potential outcome to calculate PSE
```{r}
flex_results1 <- flexEffect(p1 = list(potential_outcome1, potential_outcome2),
                            p0 = potential_outcome0, scale = "diff", CI_level = 0.95,nboot = 5)
```


# multiple treatments

## flexible paths for multiple treatments

pathfit
```{r}
data("multiTreat")
mfit<- pathsFit(data = multiTreat,
                Y = "Y",
                A = c("t1","t2","t3"),
                cov_x = "X",
                M.list = list(
                  M1 = 'm1',
                  M2 = 'm2',
                  M3 = 'm3',
                  M4 = 'm4',
                  M5 = 'm5',
                  M6 = 'm6'
                ),
                estimation = "EIF",
                model.propensity =list( ~  glm(family = binomial())),
                model.outcome = list( ~SuperLearner(SL.library = "SL.mean",family = gaussian())),
                model.iter  = list(~glm(family = gaussian()))
)
```

potential outcome for active setting
```{r}
mp1<-mflexPotential(active = list(a1=c(0,1,0,0,1,0,0),
                                  a2=c(1,0,1,1,1,0,0),
                                  a3=c(NA,NA,NA,1,0,0,0)),mfit)
mp2<-mflexPotential(active = list(a1=c(0,0,0,0,1,0,0),
                                  a2=c(0,0,0,1,1,0,0),
                                  a3=c(NA,NA,NA,1,0,0,0)),mfit)



```

PSE
```{r}
flexEffect(p1 = mp1, p0 = mp2, scale = "diff", CI_level = 0.95, nboot =2 , m.cores = 8)
```

